User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R Bayesian models of tag retrieval

### 2013-10-06 writeups/proposal/proposal.tex
foo
Former-commit-id: 5927992fe44d7b08ef715a895d9bc27c8afffc6e [formerly 74e943b3e3c789f66d4ca9f6b0ad8d83cc2d1373]
Former-commit-id: 44898ea3d19ceb94c55b1c3edb6b7010c81c07d0

A formal description of the random permutation model in \textcite{Sahlgren2008} is included in Table \ref{tabRandPermModel}.
With random permutations, each word environment vector ($e_{i}$) is a large sparse vector of zeros with a few $<1,-1>$s in random locations. 
In order to create a new environment vector for a word that preceded another word in a sentence, that word's environment vector ($e_{i}$) is bit shifted to the left one position ($^{-1}$).
This produces a new environment vector ($e_{i^{-1}}$) for the combination of the word and the position that is uncorrelated with the original word's environment vector and all other environment vectors.

@@

For random permutations, each tag is represented by a compressed vector with a length much less than the number of words.
Note that if the length of a word's environment vector was the number of unique words, then each word could be represented by associating it with a particular row in the column vector.
If done in this way, building a matrix of all words' environment vectors x tags would recover the original word x document matrix \parencite{Kanerva2000}.
However, each word's environment vector is compressed using a length much less than the number of unique words and using a combination of a few $<1,-1>$s to represent the word.

>>>>

A formal description of the random permutation model in \textcite{Sahlgren2008} is included in Table \ref{tabRandPermModel}.
With random permutations, each word environment vector ($e_{i}$) is a large sparse vector of zeros with a few $\{1,-1\}$s in random locations. 
In order to create a new environment vector for a word that preceded another word in a sentence, that word's environment vector ($e_{i}$) is bit shifted to the left one position ($^{-1}$).
This produces a new environment vector ($e_{i^{-1}}$) for the combination of the word and the position that is uncorrelated with the original word's environment vector and all other environment vectors.

@@

For random permutations, each tag is represented by a compressed vector with a length much less than the number of words.
Note that if the length of a word's environment vector was the number of unique words, then each word could be represented by associating it with a particular row in the column vector.
If done in this way, building a matrix of all words' environment vectors x tags would recover the original word x document matrix \parencite{Kanerva2000}.
However, each word's environment vector is compressed using a length much less than the number of unique words and using a combination of a few $\{1,-1\}$s to represent the word.
